Title Goes Here

### 2020-05-03 analysis/paper/paper.Rmd
we've got plots for all three confs now

```{r}
# CTRL + OPTION + i to insert a code block
library(here)
# column names should be:
# session, FirstName, AbstractTitle

SAA18 <- readxl::read_excel(here("analysis/data/raw-data/2018 SAA Title.xlsx"))
EAA18 <- readxl::read_excel(here("analysis/data/raw-data/2018 EAA.xlsx"))
CAA18 <- readxl::read_excel(here("analysis/data/raw-data/2018 CAA.xlsx"))

@@

```{r}
# make the custom functions available here in this Rmd file
source(here::here("analysis/paper/functions-for-gender.R"))
source(here::here("analysis/paper/functions-for-topic-models.R"))
```

```{r}
# let's run the topic model fn for each conf
CAA18_tm <- do_the_topic_model(CAA18, 21)
EAA18_tm <- do_the_topic_model(EAA18, 12)
SAA18_tm <- do_the_topic_model(SAA18, 21)

# Let's save the output for each one
saveRDS(CAA18_tm, here::here("analysis/data/derived-data/CAA18_topic_model.rds"))
saveRDS(EAA18_tm, here::here("analysis/data/derived-data/EAA18_topic_model.rds"))
saveRDS(SAA18_tm, here::here("analysis/data/derived-data/SAA18_topic_model.rds"))

# gender model
CAA18_gm <- get_the_gender_data(CAA18)
saveRDS(CAA18_gm, here::here("analysis/data/derived-data/CAA18_gender_model.rds"))
SAA18_gm <- get_the_gender_data(SAA18)
saveRDS(SAA18_gm, here::here("analysis/data/derived-data/SAA18_gender_model.rds"))
```

Figure \@ref(fig:demo-plot) shows how we can have a caption and cross-reference for a plot

```{r demo-inline-code}
x <- round(pi, 2)
```

Here is an example of inline code `r x` in the middle of a sentence.

>>>>

```{r}
library(here)
# column names should be:
# session, FirstName, AbstractTitle

SAA18 <- readxl::read_excel(here::here("analysis/data/raw-data/2018 SAA Title.xlsx"))
EAA18 <- readxl::read_excel(here::here("analysis/data/raw-data/2018 EAA.xlsx")) 
CAA18 <- readxl::read_excel(here::here("analysis/data/raw-data/2018 CAA.xlsx"))

@@

```{r, eval=FALSE}

# make the custom function available here in this Rmd file
source(here::here("analysis/paper/functions-for-gender.R"))

# compute gender model, take a few minutes...
SAA18_gm <- get_the_gender_data(SAA18)
saveRDS(SAA18_gm, here::here("analysis/data/derived-data/SAA18_gender_model.rds")) # ok

EAA18_gm <- get_the_gender_data(EAA18, first_name_appears_first = FALSE)
saveRDS(EAA18_gm, here::here("analysis/data/derived-data/EAA18_gender_model.rds"))

CAA18_gm <- get_the_gender_data(CAA18)
saveRDS(CAA18_gm, here::here("analysis/data/derived-data/CAA18_gender_model.rds"))
```

```{r, eval=FALSE}

# make the custom function available here in this Rmd file
source(here::here("analysis/paper/function-for-structural-topic-model.R"))

# compute and save the topic model for each conf, takes quite a long time
SAA18_stm <- 
  stm_model_and_plot(conf_paper_titles = SAA18, 
                     conf_gender_results = SAA18_gm, 
                     max.em.its = 1000)

saveRDS(SAA18_stm, here::here("analysis/data/derived-data/SAA18_topic_model_and_plot.rds"))

CAA18_stm <-   
  stm_model_and_plot(conf_paper_titles = CAA18, 
                     conf_gender_results = CAA18_gm, 
                     lower_thresh = 3,
                     max.em.its = 1000)

saveRDS(CAA18_stm, here::here("analysis/data/derived-data/CAA18_topic_model_and_plot.rds"))

EAA18_stm <- 
  stm_model_and_plot(conf_paper_titles = EAA18, 
                     conf_gender_results = EAA18_gm, 
                     first_name_appears_first = FALSE,
                     max.em.its = 1000)

saveRDS(EAA18_stm, here::here("analysis/data/derived-data/EAA18_topic_model.rds"))
